\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-01-04 manuscript.Rnw
Minor plot tweaks
Incorporate new hesim labels functionality

<<labels_indiv>>=
labs_indiv <- get_labels(hesim_dat, grp_label = NULL)
@

@@

<<ictstm_summarize>>=
library("magrittr")
ce_sim_ictstm <- ictstm$summarize()
summary(ce_sim_ictstm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

<<psm_hesim_data>>=
hesim_dat$patients <- data.table(
  patient_id = 1:4,
  grp_id = c(1, 1, 2, 2),
  patient_wt = rep(1/4, 4),
  age = c(55, 65, 55, 65),
  female = c(1, 1, 0, 0)
)
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

<<cea_icer>>=
icer(cea_pw_ictstm, k = 100000, 
     strategy_values = strategies$strategy_name[-1]) %>%
  format()
@

@@

\begin{figure}[t!]
\centering
% Cost-effectiveness plane
\begin{subfigure}[b]{.48\textwidth}
\centering
\includegraphics{figure/ce_plane-1.pdf}
\caption{Cost-effectiveness plane} \label{subfig:ce-plane}
\end{subfigure}
% CEAC (simultaneous)
\begin{subfigure}[b]{.48\textwidth}
\centering
\includegraphics{figure/ceac_simultaneous-1.pdf}
\caption{CEAC (simultaneous)} \label{subfig:ceac-simultaneous}
\end{subfigure}
\par\bigskip % Add some vertical space for second row
% CEAC (pairwise)
\begin{subfigure}[b]{.48\textwidth}
\centering
\includegraphics{figure/ceac_pw-1.pdf}
\caption{CEAC (pairwise)} \label{subfig:ceac-pw}
\end{subfigure}
% CEAF
\begin{subfigure}[b]{.48\textwidth}
\centering
\includegraphics{figure/ceaf-1.pdf}
\caption{CEAF} \label{subfig:ceaf}
\end{subfigure}
\par\bigskip % Add some vertical space for third row
% EVPI
\begin{subfigure}[b]{.48\textwidth}
\centering
\includegraphics{figure/evpi-1.pdf}
\caption{EVPI} \label{subfig:evpi}
\end{subfigure}
\caption{Representations of decision uncertainty}\label{fig:cea-plots}
\end{figure}

>>>>

<<labels_indiv>>=
labs_indiv <- get_labels(hesim_dat)
print(labs_indiv)
@

@@

<<ictstm_summarize>>=
library("magrittr")
ce_sim_ictstm <- ictstm$summarize()
summary(ce_sim_ictstm, labels = labs_indiv) %>%
  format()
@

@@

<<psm_hesim_data>>=
hesim_dat$patients <- data.table(
  patient_id = 1:4,
  grp_id = c(1, 1, 2, 2),
  patient_wt = rep(1/4, 4),
  age = c(55, 65, 55, 65),
  female = c(1, 1, 0, 0),
  grp_name = rep(c("Female", "Male"), 
                 each = 2)
)
@

<<labels_cohort>>=
labs_cohort <- get_labels(hesim_dat)
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm, labels = labs_cohort) %>%
  format()
@

@@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm, labels = labs_cohort) %>%
  format()
@

@@

<<cea_icer>>=
icer(cea_pw_ictstm, k = 100000, labels = labs_indiv) %>%
  format()
@

@@

\begin{figure}[t!]
\centering
% Cost-effectiveness plane
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ce_plane-1.pdf}
\caption{Cost-effectiveness plane} \label{subfig:ce-plane}
\end{subfigure}
% CEAC (simultaneous)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-1.pdf}
\caption{CEAC (simultaneous)} \label{subfig:ceac-simultaneous}
\end{subfigure}
\par\bigskip % Add some vertical space for second row
% CEAC (pairwise)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-2.pdf}
\caption{CEAC (pairwise)} \label{subfig:ceac-pw}
\end{subfigure}
% CEAF
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceaf-1.pdf}
\caption{CEAF} \label{subfig:ceaf}
\end{subfigure}
\par\bigskip % Add some vertical space for third row
% EVPI
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/evpi-1.pdf}
\caption{EVPI} \label{subfig:evpi}
\end{subfigure}
\caption{Representations of decision uncertainty}\label{fig:cea-plots}
\end{figure}
